Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-22 paper.tex
improved RP5 description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

{\textbf{(RP5)} Although ESBMC \cite{Cordeiro12} was extended to support C/C++ and some variants, new application interfaces and programming languages are often developed, which require suitable software verification tools. Indeed, it would be interesting if a new programming language model could be loaded, which along with a BMC core could check different programs. Some work towards that was already presented by Sousa, Cordeiro, and Filho~\cite{Garcia16}, which employed operational models for checking Qt-based programs from consumer electronics. In summary, the BMC core (in that case, ESBMC) is not changed, but instead an operational model, which implements the behavior and features of Qt libraries, is used for providing the new code structure to be checked. \textcolor{red}{nao deveriamos falar que no pior caso poderiamos traduzir para c? aqui nao deveriamos mencionar o trabalho do januario?} Such research problem is closely related to the first one \textbf{(RP1)} and has the potential to devise a new paradigm in software verification.

@@

%77
\bibitem{Jackson16}
Jackson D., Vaziri M.:
\newblock {\em{ Correct or usable? the limits of traditional verification (impact paper award)}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 11, 2016.

%78
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Handling unbounded loops with {ESBMC} 1.20}}.
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%79
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%80
\bibitem{Haran15}
Haran A., Carter M., Emmi M., Lal A., Qadeer S., Rakamaric Z.:
\newblock {\em{ SMACK+Corral: A Modular Verifier - (Competition Contribution)}}. 
\newblock In: 21st International Conference Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 451--454, 2015.

%81
\bibitem{Beyer16}
Beyer, D.:
\newblock {\em{ Reliable and Reproducible Competition Results with BenchExec and Witnesses (Report on SV-COMP 2016)}}. 
\newblock In: 22nd International Conference Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9636, pp. 887--904, 2016.

%82
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%83
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.

%84
\bibitem{antennasbrt}
de Jesus A. S., rodrigues R. N., Ferreira A. N. G., Valente V. H., de Melo W. C., de Lima Filho E. B, da Silva J\'unior W. S.:
\newblock {\em{Automatic Antenna Alignment System for Satellite Receivers Operating in C and Ku Bands}}. 
\newblock To appear in: Brazilian Symposium on Telecommunications and Signal Processing, pp. 1-5, 2017. (in Portuguese)

\bibitem{amoedo}
Amoedo D. A., da Silva J\'unior W. S., de Lima Filho E. A.:
\newblock {\em{Parameter Selection for SVM in Automatic Modulation Classification of Analog and Digital Signals}}. 
\newblock In: International Telecommunications Symposium (ITS), pp. 1-5, 2014.

\bibitem{mlswverif}
L Hamel:
\newblock {\em {On the Use of Machine Learning in Formal Software Verification.}} 
\newblock {Technical Report TR03-294, Dept. of Computer Science and Statistics, University of Rhode Island}, 2003.

\bibitem{nguyen}
L Hamel:
\newblock {\em {The Application of Machine Learning Methods in Software Verification and Validation.}} 
\newblock {University of Texas at Austin, master of science dissertation}, 2010.

>>>>

{\textbf{(RP5)} Although ESBMC \cite{Cordeiro12} was extended to support C/C++ and some variants, new application interfaces and programming languages are often developed, which require suitable software verification tools. Indeed, it would be interesting if a new programming language model could be loaded, which along with a BMC core could check different programs. Some work towards that was already presented by Sousa, Cordeiro, and Filho~\cite{Garcia16}, which employed operational models for checking Qt-based programs from consumer electronics. In summary, the BMC core (in that case, ESBMC) is not changed, but instead an operational model, which implements the behavior and features of Qt libraries, is used for providing the new code structure to be checked. This approach could adopt the clang compiler~\cite{Lopes:2014:GSL:2692607}, which is already widely used in industry~\cite{clang-usage}, in order to produce an Abstract Syntax Tree (AST) for a given programming language ({\it e.g.}, C/C++/ObjectiveC/ObjectiveC++). This AST can then be converted either to an intermediate representation (IR) of the underlying verifier or to LLVM bitcode that is already produced by clang. Such research problem is closely related to the first one \textbf{(RP1)} and has the potential to devise a new paradigm in software verification.

@@

%77
\bibitem{Lopes:2014:GSL:2692607}
Bruno~Cardoso Lopes and Rafael Auler.
\newblock {\em Getting Started with LLVM Core Libraries}.
\newblock Packt Publishing, 2014.

%78
 \bibitem{clang-usage}
Cade Metz.
\newblock Why {A}pple?s swift language will instantly remake computer
  programming, 204.
\newblock http://www.wired.com/2014/07/apple-swift/.

%79
\bibitem{Jackson16}
Jackson D., Vaziri M.:
\newblock {\em{ Correct or usable? the limits of traditional verification (impact paper award)}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 11, 2016.

%80
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Handling unbounded loops with {ESBMC} 1.20}}.
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%81
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%82
\bibitem{Haran15}
Haran A., Carter M., Emmi M., Lal A., Qadeer S., Rakamaric Z.:
\newblock {\em{ SMACK+Corral: A Modular Verifier - (Competition Contribution)}}. 
\newblock In: 21st International Conference Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 451--454, 2015.

%83
\bibitem{Beyer16}
Beyer, D.:
\newblock {\em{ Reliable and Reproducible Competition Results with BenchExec and Witnesses (Report on SV-COMP 2016)}}. 
\newblock In: 22nd International Conference Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9636, pp. 887--904, 2016.

%84
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%85
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.

%86
\bibitem{antennasbrt}
de Jesus A. S., rodrigues R. N., Ferreira A. N. G., Valente V. H., de Melo W. C., de Lima Filho E. B, da Silva J\'unior W. S.:
\newblock {\em{Automatic Antenna Alignment System for Satellite Receivers Operating in C and Ku Bands}}. 
\newblock To appear in: Brazilian Symposium on Telecommunications and Signal Processing, pp. 1-5, 2017. (in Portuguese)

%87
\bibitem{amoedo}
Amoedo D. A., da Silva J\'unior W. S., de Lima Filho E. A.:
\newblock {\em{Parameter Selection for SVM in Automatic Modulation Classification of Analog and Digital Signals}}. 
\newblock In: International Telecommunications Symposium (ITS), pp. 1-5, 2014.

%88
\bibitem{mlswverif}
L Hamel:
\newblock {\em {On the Use of Machine Learning in Formal Software Verification.}} 
\newblock {Technical Report TR03-294, Dept. of Computer Science and Statistics, University of Rhode Island}, 2003.

%89
\bibitem{nguyen}
L Hamel:
\newblock {\em {The Application of Machine Learning Methods in Software Verification and Validation.}} 
\newblock {University of Texas at Austin, master of science dissertation}, 2010.
